The complex network of trophic interactions in a subAntarctic Marine Protected

### 2023-01-27 MS_ToSubmit/MS_Burdwood_foodweb.Rmd
Continue w/ Intro

In the subAntarctic region, the level of protection is mainly associated to islands, such as South Georgia and the South Sandwich, Bouvet, Prince Edward, and Macquarie [@IUCN2023]. Interestingly, the case of the MPA Namuncurá - Banco Burdwood I (MPA N-BB), which forms the focus of this work, is unique since it is associated to a submarine plateau [@Reta2014]. Here it's noteworthy to mark that this MPA is part of a network of protected areas in the subAntarctic (i.e MPA Namuncurá - Banco Burdwood II and Yaganes), that contribute to protect and strengthen the functioning of this southern region to maintain global ocean health.

@@

Many of these MPAs centre on the presence of particularly vulnerable, keystone, or charismatic species; the presence of large numbers (or proportions) of endemic species; and the presence of high biodiversity across taxonomic levels [@Hogg2016]. Indeed, the MPA N-BB has been created because it is considered a biodiversity hotspot, mostly of its benthic community [@Schejter2016; @Falabella2017]. This community is characterized by a high biomass of vulnerable and fragile species (mainly Porifera and Cnidaria) that meet the characteristics of vulnerable marine ecosystems [@Schejter2021], here defined as sites that present taxa with a minimum biomass of 10 kg per 1200 m^2^ [@CommissionfortheConservationofAntarcticMarineLivingResources2009]. Also, it provides habitat to several small-sized species [@Lopez-Gappa2018; @MartinSirito2019; @Schejter2019], and has an important role in the life history of fishes as a food source, refuge, or nursery area [@GarciaAlonso2018; @Delpiani2020; @Troccoli2020]. The maintenance of this singular community is related to the oceanographic processes, including the circulation of the rich Malvinas (Falkland) current in the area [@Piola1989; @Guerrero1999] and the upwelling and mixing phenomena [@Matano2019]. The input of nutrients coming from the Malvinas (Falkland) current supports the plankton community [@Guinder2020]. Overall, at the ecosystem level the MPA N-BB is ascribed as a carbon-sinker [@Bergagna2019].

@@

We found that BC and BB have a more pronounced WW structure compared to CA. We identified species at mid to low trophic positions that play a key role in the trophodynamics of each marine area (e.g. Fuegian sprat Sprattus fuegensis, longtail southern cod Patagonotothen ramsayi and squat lobster Munida gregaria) and considered them as the most plausible WW species. The identification of the most influential species within food webs has become a crucial task for conservation purposes in local and regional contexts to maintain ecosystem integrity and the supply of ecosystem services for the southwestern South Atlantic Ocean. [@Riccialdelli2020]

@@

@@

* Objective
In the present work we present the first, detailed analysis of the food web for the MPA N-BB ecosystem. For this we applied a network approach to a highly-resolved food web. The objective was twofold: characterise the food web in terms of complexity and structure, and describe the species' role in such network framework.

@@

>>>>

In the subAntarctic region, the level of protection is mainly associated to oceanic islands, such as South Georgia and the South Sandwich, Bouvet, Prince Edward, and Macquarie [@IUCN2023]. Interestingly, the case of the MPA Namuncurá - Banco Burdwood I (MPA N-BB), which forms the focus of this work, is unique since it is associated to a submarine plateau [@Reta2014]. Added to this, such MPA is part of a network of protected areas in the subAntarctic (i.e joining MPAs Namuncurá - Banco Burdwood II and Yaganes), that contribute to protect and strengthen the functioning of this southern region to maintain global ocean health.

@@

Many of these MPAs centre on the presence of particularly vulnerable, keystone, or charismatic species; the presence of large numbers (or proportions) of endemic species; and the presence of high biodiversity across taxonomic levels [@Hogg2016]. Indeed, the MPA N-BB has been created because it is considered a biodiversity hotspot, mostly of its benthic community [@Schejter2016; @Falabella2017]. It is characterized by a high biomass of vulnerable and fragile species (mainly Porifera and Cnidaria) that meet the characteristics of vulnerable marine ecosystems [@Schejter2021], here defined as sites that present taxa with a minimum biomass of 10 kg per 1200 m^2^ [@CommissionfortheConservationofAntarcticMarineLivingResources2009]. Also, the benthic community provides habitat to several small-sized species [@Lopez-Gappa2018; @MartinSirito2019; @Schejter2019], and has an important role in the life history of fishes as a food source, refuge, or nursery area [@GarciaAlonso2018; @Delpiani2020; @Troccoli2020]. The maintenance of this singular community is related to the oceanographic processes, including the circulation of the rich Malvinas (Falkland) current in the area [@Piola1989; @Guerrero1999] and the upwelling and mixing phenomena [@Matano2019]. The input of nutrients coming from the Malvinas (Falkland) current also supports a diverse plankton community [@Guinder2020]. Overall, 811 benthic and planktonic species have been identified for the MPA N-BB ecosystem, where 349 were reported for the first time for the MPA [@APN2022]. At the ecosystem level the MPA N-BB is ascribed as a carbon-sinker [@Bergagna2019].

@@

The structure and functioning of ecosystems can be successfully described by studying one of the most-frequent interactions occurring between species: the predator-prey relationship [@Bascompte2009]. The predator-prey or trophic interactions of a particular region are commonly referred as the food web, that represents the roadmap for matter and energy flow in an ecosystem.
The trophic structure of the southwestern South Atlantic Ocean has been proposed to be under a 'wasp-waist' control, meaning that the structure and dynamics of the ecosystem is regulated primarily by mid-trophic level species (e.g. fishes, crustaceans) [@Padovani2012; @Saporiti2015; @Riccialdelli2020]. In particular, the ecosystem of the MPA N-BB shows a more pronounced 'wasp-waist' structure than other subAntarctic areas, like the Atlantic coast of Tierra del Fuego, where the Fuegian sprat *Sprattus fuegensis* and longtail southern cod *Patagonotothen ramsayi* are considered the most plausible 'wasp-waist' species [@Riccialdelli2020].
Recently, the identification of the most influential species within food webs has become a crucial task for conservation purposes in local and regional contexts to maintain ecosystem integrity and the supply of ecosystem services for the southwestern South Atlantic Ocean [@Franco2020; @Bergagna2020; @Riccialdelli2020].

@@

In the past decades, several researches have shown that high-latitude marine ecosystems, such as the MPA N-BB, are characterised by an unexpected complexity in terms of biodiversity and ecological interactions [@Day2013; @Kortsch2019; @Cordone2020; @Trathan2021].

@@

* Objective

In the present work we present the first, detailed analysis of the food web for the MPA N-BB ecosystem. For this we applied a network approach to a highly-resolved food web. The objective was twofold: characterise the food web in terms of complexity and structure, and describe the species' role in such network framework.

@@

# Acknowledgements

This study was funded by Consejo Nacional de Investigaciones Científicas y Técnicas (CONICET) and Agencia Nacional de Promoción Científica y Tecnológica (PICT 2020-SERIEA-01617). This work is contribution no. XX of the MPA Namuncurá (Law 26875).
